Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-13 VMCAI-revised-version/final.tex
section

Several families of formal models of processes give rise to WSTSs in a natural way, e.g. Petri nets when inclusion between markings is used as the well-ordering and lossy channel systems with the subword ordering.

>>>>

Several families of formal models of processes give rise to WSTSs in a natural way with disfferent compatibilities, e.g. compatible counter machines like VASS with $d$ counters and $Q$ a finite set of control-states (and equivalently Petri nets and data Petri nets), reset/transfer VASS are WSTS with strong compatibility for the usual ordering $=\times \leq^d$ on the set of states $S=Q \times \N^d$.
Similarly, lossy channel systems with $d$ channels and $Q$ a finite set of control-states are WSTS (with a non-strong compatibility)
for the ordering $=\times \sqsubseteq^d$ (where $\sqsubseteq$ is the subword ordering on $\Sigma^*$) on $S= Q \times (\Sigma^*)^d$.\\
%%%%

By applying Proposition 4.3 from \cite{DBLP:journals/corr/abs-1208-4549}, we can reintroduce a straightforward definition of a specific proper subset of wqos that possesses an excellent characteristic that allows to obtain more algorithms:

\begin{definition}
A wqo $(X, \leq)$ is an \emph{$\omega^2$-wqo} if $(Ideals(X), \subseteq)$ forms a wqo.
\end{definition}

%Using Proposition 4.3 in \cite{DBLP:journals/corr/abs-1208-4549}, we recall a simple definition of a strict subclass of wqos that has a very nice property: a wqo $(X,\leq)$ is an $\omega^2$-wqo iff $(Ideals(X),\subseteq)$ is a wqo.

Although there exists wqo that are not $\omega^2$-wqo (see the Rado ordering in \cite{DBLP:journals/ipl/Jancar99}), all naturally occurring wqos are $\omega^2$-wqo, perhaps to the notable exception of ﬁnite graphs quasi-ordered by the graph minor relation, which are wqo but not known to be $\omega^2$-wqo. The class of $\omega^2$-wqo is robust because every datatype in the following list - natural number, finite set, ﬁnite product, ﬁnite sum, finite disjoint sum, ﬁnite words, ﬁnite multisets and ﬁnite trees - is a an $\omega^2$-wqo (Proposition 4.5 in \cite{DBLP:journals/corr/abs-1208-4549}). Now we are able to define $\omega^2$-WSTS:

\begin{definition} \cite{DBLP:journals/corr/abs-1208-4549}
A WSTS  $\mathscr{S}=(S, \rightarrow, \leq)$
is an $\omega^2$-WSTS if $(S, \leq)$ is an $\omega^2$-wqo.
\end{definition}
Since almost of usual wqo are $\omega^2$-wqo, all naturally occurring WSTS are in fact $\omega^2$-WSTS: for example, reset/transfer VASS are $\omega^2$-WSTS.\\
%%%%%%
